---
output: rmarkdown::github_document
---

# aws.athena

Access Amazon's AWS Athena API

## Description

Reticulated wrapper for the Python 'boto3' Athena client library.

## NOTE

This package **requires** Python >= 3.5 to be available and the `boto3` Python package.

## What's Inside The Tin

The following functions are implemented:

- `create_named_query`:	Create a named query.
- `delete_named_query`:	Delete a named query.
- `get_named_query`:	Get Query Execution
- `get_named_queries`:	Get Query Execution (batch/multiple)
- `get_query_execution`:	Get Query Execution
- `get_query_executions`:	Get Query Executions (batch/multiple)
- `list_named_queries`:	List Named Queries
- `list_query_executions`:	List Query Executions
- `start_query_execution`:	Start Query Execution
- `stop_query_execution`:	Stop Query Execution

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/aws.athena")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(aws.athena)

# current verison
packageVersion("aws.athena")

```

